Measurement and Probability in Fuzzy Quantum Theories

### 2017-01-19 prop.tex
prop.tex \section{Increasing the Measurement Resource} Updating...

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
In general, each two 1-dimensional projectors~$\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$ might
be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are normalized,
when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
when there is no confusion.

\yutsung{Just notice that I only focus on $\mathbb{R}^{3}$ instead
of $\mathbb{C}^{3}$. Although this might be just tedious details
in this approach, still need to verify carefully.}}. Therefore, the set of 1-dimensional projectors mapping to impossible,
denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
plays an important role to understand $\bar{\mu}$. There are 4 different
cases when analyzing $\bar{\mu}^{-1}\left(\imposs\right)$:
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$ because $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
is inconsistent with $\bar{\mu}(\proj{\psi_{0}'})=\bar{\mu}(\proj{\psi_{1}'})=\imposs$
and $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
with $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$.
Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states in core.

@@

>>>>

In example~\ref{ex:three-dimensional-three-value} and \ref{ex:three-dimensional-4-value},
although quantum IVPMs have empty cores, we might think that the probability
measure~$\bar{\mu}$ is induced by some states. In example~\ref{ex:three-dimensional-three-value},
the probability measure $\bar{\mu}$ might be induced by the state
$\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$,
or induced by the state $\ket{1}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$.
In example~\ref{ex:three-dimensional-4-value}, the probability measure
$\bar{\mu}$ might be induced by the state $\ket{2}$ because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$.
In general, each two real 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to impossible suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$\footnote{Notice that we only discuss only discuss real 1-dimensional projectors
in the Hilbert space of dimension 3. In general, we could discuss
all 1-dimensional projectors in any dimension. However, restricting
to $\mathbb{R}^{3}$ enable us to use cross product which will simplify
our discussion a lot, and $\mathbb{R}^{3}$ is easy to visualize and
imagine. Also, if a quantum IVPM~$\bar{\mu}$ has an empty core when
restricting to $\mathbb{R}^{3}$, $\bar{\mu}$ has an empty core on
the original space as well. So restricting on real 1-dimensional projectors
still provides valid results.

About the cross product, even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$
are normalized, when they are not orthogonal, $\ket{\psi_{0}}\times\ket{\psi_{1}}$
is not normalized. We will use $\ket{\psi_{0}}\times\ket{\psi_{1}}$
and the normalized $\ket{\psi_{0}}\times\ket{\psi_{1}}$ interchanged
when there is no confusion.}. Therefore, the set of 1-dimensional projectors mapping to impossible,
denoted by $\bar{\mu}^{-1}\left(\imposs\right)=\set{\ket{\psi}\in\mathbb{C}^{3}}{\bar{\mu}(\proj{\psi})=\imposs}$,
plays an important role to understand $\bar{\mu}$. There are 4 different
cases when analyzing $\bar{\mu}^{-1}\left(\imposs\right)$:
\begin{enumerate}
\item If another pair of states~$\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$
gives different state of cross product~$\ket{\psi_{0}'}\times\ket{\psi_{1}'}$,
then both $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
might induce $\bar{\mu}$, but neither $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
nor $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ in the core
of $\bar{\mu}$ because $\mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}$
is inconsistent with $\bar{\mu}(\proj{\psi_{0}'})=\bar{\mu}(\proj{\psi_{1}'})=\imposs$
and $\mu_{\ket{\psi_{0}'}\times\ket{\psi_{1}'}}^{B}$ is inconsistent
with $\bar{\mu}(\proj{\psi_{0}})=\bar{\mu}(\proj{\psi_{1}})=\imposs$.
Actually, $\bar{\mu}$ has an empty core. 
\item If $\ket{\psi_{0}}\times\ket{\psi_{1}}$ and $\ket{\psi_{0}'}\times\ket{\psi_{1}'}$
always represent the same state for all $\ket{\psi_{0}'}$ and $\ket{\psi_{1}'}\in\bar{\mu}^{-1}\left(\imposs\right)$,
then $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is the only pure state
which might induce $\bar{\mu}$. In another word, if $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, then $\ket{\phi}$ and $\ket{\psi_{0}}\times\ket{\psi_{1}}$
represent the same state. 
\item $\bar{\mu}^{-1}\left(\imposs\right)$ may contain only one state~$\ket{\psi_{0}}$.
In this case, $\ket{\psi_{0}}\times\ket{\psi_{1}}$ is undefined.
If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$ for some
pure state~$\ket{\phi}$, $\ket{\phi}$ could be any state orthogonal
to $\ket{\psi_{0}}$.
\item $\bar{\mu}^{-1}\left(\imposs\right)=\emptyset$. If $\mu_{\phi}^{B}\in\mathrm{core}\left(\bar{\mu}\right)$
for some pure state~$\ket{\phi}$, we could say nothing about $\ket{\phi}$.
\end{enumerate}
In summary, if we have an idea of $\bar{\mu}^{-1}\left(\imposs\right)$,
we could have some idea of the pure states in core.

@@

In order to simplify the discussion, let's set the center of $\bar{\mu}^{-1}\left(\imposs\right)$
as the north pole, and assume $\bar{\mu}$ maps every state whose
latitude is larger than $\theta_{0}$ to impossible. In order to simplify
the notation, let's give the following definition.

\begin{definition}Given a vector~$\ket{\psi}\in S^{2}$ with a specified
north pole~$\ket{0}\in S^{2}$, then $\theta\left(\ket{\psi}\right)=\arccos\ip{0}{\psi}$
denotes the the latitude of $\ket{\psi}$.\end{definition}
